\documentclass[a4paper,10pt]{article}

\usepackage[top=0.4in, bottom=0.4in, left=0.5in, right=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{parskip}
\usepackage{fontawesome5}

\pagenumbering{gobble}

% Reduce paragraph spacing
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}

% Section formatting – compact
\titleformat{\section}{
  \normalsize\bfseries\uppercase
}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{4pt}

\setlist[itemize]{noitemsep, topsep=1pt, leftmargin=12pt, parsep=0pt}

\begin{document}

%====================
% HEADER
%====================

\begin{center}
    {\LARGE \textbf{Mateus Gündel}} \\[2pt]
    {\normalsize Senior Data Engineer} \\[4pt]
    \small
    \faEnvelope\ \href{mailto:mateus8923@gmail.com}{mateus8923@gmail.com} \quad
    \faPhone\ +34 678 237 119 \quad
    \faMapMarker\ Granada, Spain \\
    \faLinkedin\ \href{https://linkedin.com/in/mateusgundel}{linkedin.com/in/mateusgundel} \quad
    \faGithub\ \href{https://github.com/MateusGundel}{github.com/MateusGundel}
\end{center}

\vspace{2pt}

%====================
% PROFILE
%====================

\section*{Profile}

\small
Data engineer with 6+ years of experience designing scalable architectures, building reliable ETL/ELT pipelines, and enabling data-driven decision-making across marketing and product domains. Deep expertise in Databricks, Apache Spark, and cloud-based data platforms. Comfortable in client-facing environments and cross-functional collaboration. Currently pursuing a Master's degree focused on Artificial Intelligence and Industrial Systems.

%====================
% CORE EXPERTISE
%====================

\section*{Core Expertise}
\vspace{-10pt}
\small
\begin{multicols}{3}
\begin{itemize}[leftmargin=10pt, label=\raisebox{0.3ex}{\tiny\faChevronRight}]
    \item Data Architecture Design
    \item ETL/ELT Pipeline Design
    \item Medallion Architecture
    \item Data Integration Strategy
    \item Batch \& Streaming Processing
    \item Data Modeling \& Governance
    \item Marketing Analytics
    \item Cross-Platform Consolidation
    \item Stakeholder Communication
\end{itemize}
\end{multicols}


%====================
% PROFESSIONAL EXPERIENCE
%====================

\section*{Professional Experience}

\small
\textbf{Senior Data Engineer} \hfill Dec 2024 -- Present \\
\textit{Sicredi -- Marketing Data Team, Financial Sector}

\begin{itemize}
    \item Design and orchestrate scalable data pipelines on Databricks (Apache Spark, Auto Loader for incremental ingestion, CDC for change data capture) with CI/CD managed through GitLab on AWS-backed infrastructure.
    \item Build a 360° view of brand metrics and marketing actions by integrating paid and organic data from multiple ad platforms (Meta, Google, TikTok, LinkedIn, Bing, and others) via Sprinklr and Supermetrics.
    \item Ingest and consolidate partner and third-party data sources to enrich marketing analytics.
    \item Own the data modeling and governance strategy, serving as the go-to technical authority for cross-functional teams on data standards, lineage, and best practices.
    \item Deliver reliable datasets to BI tools (Power BI, Denodo) supporting data-driven decisions.
\end{itemize}

\vspace{4pt}

\textbf{Data Engineer} \hfill Mar 2020 -- Dec 2024 \\
\textit{Compass.uol -- Technology Consulting}

\begin{itemize}
    \item Outsourced to Sicredi's BI team as a Full Stack Python Developer, building a load management platform for non-technical users.
    \item Maintained and optimized Oracle procedures and packages supporting critical data workflows.
    \item Transitioned to a new team within Sicredi to lead the Databricks deployment for a business domain, bringing marketing data into the data lake.
    \item Automated ingestion processes and managed enterprise data integrations using ODI, CKAN, and Denodo.
\end{itemize}

\vspace{4pt}

\textbf{Full Stack Software Developer} \hfill Jul 2018 -- Mar 2020 \\
\textit{Velsis -- Road Infrastructure \& Traffic Systems}

\begin{itemize}
    \item Developed computer vision solutions (OCR, object detection) using Python and TensorFlow.
    \item Contributed to radar system development using Java, PostgreSQL, and AngularJS.
    \item Containerized and deployed traffic monitoring applications using Docker and GitLab CI/CD.
\end{itemize}

\vspace{2pt}

%====================
% EDUCATION
%====================

\section*{Education}

\small
\textbf{Master's Degree in Industrial Systems and Processes} \hfill 2024 -- Present \\
\textit{Universidade de Santa Cruz do Sul (UNISC)}

\vspace{4pt}

\textbf{Bachelor's Degree in Computer Engineering} \hfill 2017 -- 2023 \\
\textit{Universidade de Santa Cruz do Sul (UNISC)}

\vspace{2pt}

%====================
% TECHNICAL SKILLS & CERTIFICATIONS
%====================

\section*{Technical Skills}

\small
\begin{tabularx}{\textwidth}{@{}l X@{}}
\textbf{Programming:} & Python, SQL, Bash/Shell, Java, JavaScript \\
\textbf{Data Engineering:} & Databricks, Apache Spark, Delta Lake, Unity Catalog, ODI, Denodo \\
\textbf{Cloud \& DevOps:} & AWS, Azure, Terraform, Docker, Git, GitLab CI/CD \\
\textbf{ML \& Vision:} & TensorFlow, OpenCV, Neural Networks \\
\end{tabularx}

\vspace{2pt}

%====================
% CERTIFICATIONS
%====================

\section*{Certifications}

\small
\textbf{AWS Certified Cloud Practitioner} -- Amazon Web Services \hfill Dec 2021 \\
\textbf{PCEP -- Certified Entry-Level Python Programmer} -- Python Institute \hfill Oct 2020

\vspace{2pt}

%====================
% LANGUAGES
%====================

\section*{Languages}

\small
Portuguese (Native) \quad\textbar\quad English (B2 -- Professional) \quad\textbar\quad Spanish (A2 -- Basic)

\end{document}